`treats`: a modular `R` package for simulating trees and traits.

### 2023-06-01 paper/treats_paper.Rmd
Update treats_paper.Rmd

<!-- no more than 3000-4000 words total -->

$^1$ School of Biosciences, University of Sheffield, Sheffield, S10 2TN, United Kingdom. guillert@tcd.ie

>>>>

<!-- no more than 3000-4000 words total -->
<!-- The code checklist must be filled in and uploaded as a 'File for editors'.  -->
$^1$ School of Biosciences, University of Sheffield, Sheffield, S10 2TN, United Kingdom. guillert@tcd.ie

Running head:
`treats`: TREes And Traits Simulations
